The design and implementation of standards-based Grid single sign-on using federated identity

### 2009-05-01 doc/sec/papers/GRID09/paper.tex
More plot; tex change comes soon

\begin{figure}
\includegraphics[width=0.9\columnwidth]{SAML2SSO_thread10.pdf}
\caption{Performance of HED echoString services with SAMLSSO profile: 1 service
and 10 clients}
\label{fig:SAML2SSO_thread10}
\end{figure}

@@

Figure \ref{fig:SAML2SSO_thread10} depicts the average response time and
throughputs for 10 clients running simultaneously against the ``echoString'' service enhanced with SAML2SSO
profile. Since the success of authentication from IdP can be regarded as valid for the whole
session between client and service, the client with ``Session reused'' need to accomplish the SAML2SSO
profile only once for all SOAP invocations on this client, while the client with ``Session
non-reused'' will need to accomplish this profile once per SOAP invocation.

>>>>

\begin{figure}
\includegraphics[width=0.9\columnwidth]{SAML2SSO_thread10_nosso.pdf}
\caption{Performance of HED echoString services with SAMLSSO profile: 1 service
and 10 clients}
\label{fig:SAML2SSO_thread10_nosso}
\end{figure}

\begin{figure}
\includegraphics[width=0.9\columnwidth]{SAML2SSO_thread10_nosso_and_sso.pdf}
\caption{Performance of HED echoString services with SAMLSSO profile: 1 service
and 10 clients}
\label{fig:SAML2SSO_thread10_nosso_and_sso}
\end{figure}

@@

Figure \ref{fig:SAML2SSO_thread10_nosso} depicts the average response time and
throughputs for 10 clients running simultaneously against the ``echoString'' service enhanced with SAML2SSO
profile. Since the success of authentication from IdP can be regarded as valid for the whole
session between client and service, the client with ``Session reused'' need to accomplish the SAML2SSO
profile only once for all SOAP invocations on this client, while the client with ``Session
non-reused'' will need to accomplish this profile once per SOAP invocation.
